---
output: html_document
editor_options: 
  chunk_output_type: inline
---
# Fit spatial temporal models to bottom temperature

```{r setup}
library(tidyverse)
library(sdmTMB)
# library(future)
library(dplyr)
library(gfvelocities)

plot_map_raster <- function(dat, column = "est") {
    ggplot(dat, aes_string("X", "Y", fill = column)) +
    geom_raster() +
    coord_fixed()+
gfplot::theme_pbs() + theme(
  axis.title = element_blank(), 
  axis.ticks = element_blank(),
  axis.text = element_blank()
  )
}
```

Model diagnostics function
```{r}
get_diag <- function(m, response = "temperature_c", variable = "depth_scaled", colour_var = "depth", start_year = 2007, ssids = c(1,3,4,16)) {
  predictions <- predict(m)
  predictions$residuals <- residuals(m)
  
  predictions <- predictions %>% filter (year >= start_year)
  
  plot_map <- function(dat, column = "est") {
    ggplot(dat, aes_string("X", "Y", colour = column)) +
      geom_point() +
      coord_fixed()+
      gfplot::theme_pbs() 
  }

  g <- plot_map(predictions, "est") +
    scale_colour_viridis_c() +
    ggtitle("Prediction (fixed effects + all random effects)")
  print(g)

  g <- plot_map(predictions, "est_non_rf") +
    ggtitle("Prediction (fixed effects only)") +
    scale_colour_viridis_c()
  print(g)

  g <- plot_map(predictions, "est_rf") +
    ggtitle("All random effects only") +
    scale_colour_gradient2()
  print(g)

  g <- plot_map(predictions, "omega_s") +
    ggtitle("Spatial random effects only") +
    scale_colour_gradient2()
  print(g)

  g <- plot_map(predictions, "epsilon_st") +
    ggtitle("Spatiotemporal random effects only") +
    facet_wrap(~year) +
    scale_colour_gradient2()
  print(g)

  g <- ggplot(predictions, aes_string("est", response)) +
    geom_point(alpha = 0.2) +
    facet_wrap(~year) +
    coord_fixed() +
    geom_abline()+
    gfplot::theme_pbs() 
  print(g)

  g <- ggplot(predictions, aes(est, residuals)) +
    geom_point(alpha = 0.2) +
    geom_smooth()+
    gfplot::theme_pbs() 
  print(g)
  
  g <- ggplot(predictions, aes_string(variable, "residuals", colour = colour_var)) +
    geom_point(alpha = 0.4, size = 1.2) +
    geom_smooth(colour="grey", size = 1.2) +
    scale_colour_viridis_c(option = "B", direction = -1, begin = 0, end = 0.7, 
      limits= c(min(predictions[colour_var]), max(predictions[colour_var]))) + #, trans= sqrt
    # facet_wrap(~year, scales = "free_x")+
    gfplot::theme_pbs() + theme(
      axis.text.y = element_text(size = 14),
      axis.text.x = element_blank(), axis.ticks.x = element_blank())
  print(g)
  
  g <- ggplot(predictions, aes_string(variable, "residuals", colour = colour_var)) +
    geom_point(alpha = 0.4, size = 0.7) +
    geom_smooth(colour="grey", size = 0.7) +
    scale_colour_viridis_c(option = "B", direction = -1, begin = 0, end = 0.7, 
      limits= c(min(predictions[colour_var]), max(predictions[colour_var]))) + #, trans= sqrt
    facet_wrap(~year, scales = "free_x")+
    gfplot::theme_pbs() + theme(axis.text.x = element_blank(), axis.ticks.x = element_blank())
  print(g)

    g <- ggplot(filter(predictions, ssid %in% ssids), aes_string(variable, "residuals", colour = colour_var)) +
    geom_point(alpha = 0.4, size = 1) +
    geom_smooth(colour="grey", size = 1) +
    scale_colour_viridis_c(option = "B", direction = -1, begin = 0, end = 0.7, 
      limits= c(min(predictions[colour_var]), max(predictions[colour_var]))) + #, trans= sqrt
    facet_wrap(~ssid, scales = "free_x")+
    gfplot::theme_pbs() 
  print(g)
  
  g <- ggplot(predictions, aes(X, Y, colour = residuals)) +
    geom_point(alpha = 0.2) +
    coord_fixed() +
    scale_color_gradient2() +
    facet_wrap(~year)+
    gfplot::theme_pbs() 
  print(g)

  aic <- function(m) {
    k <- length(m$model$par)
    nll <- m$model$objective
    2 * k - 2 * (-nll)
  }

  print("R^2:")
  r2 <- cor(predictions$est, predictions[[response]])^2
  print(r2)

  print("")
  print("AIC:")
  print(aic(m))
}
```

Load data if not using SST
```{r}
all_sensor <- readRDS(here::here("analysis/tmb-sensor-explore/data/dat-sensor-trawl-processed.rds")) # no SST

all_depth <- all_sensor %>%
  # filter(depth_max>10) %>% # maybe we should filter incase missing depth values also indicate a sensor fail?
  # filter missing location data and trial year
  dplyr::filter(!is.na(latitude), !is.na(longitude)) %>%

  # convert lat and lon to UTMs
  dplyr::mutate(X = longitude, Y = latitude) %>%
  gfplot:::ll2utm(., utm_zone = 9) %>% 

  # interpolate missing depth values
  dplyr::rename(depth = depth_m) %>%
  gfplot:::interp_survey_bathymetry()

d_trawl <- all_depth$data %>% 
  # remove obvious sensor fails, d_trawl %>% filter(depth_max<10), fishing event ids = 481861, 2179089
  filter(depth_max>10) %>% 
  gfplot:::scale_survey_predictors()

d_trawl <- d_trawl[!is.na(d_trawl$depth), ]
d_trawl <- d_trawl[!is.na(d_trawl$temperature_c), ]

d_trawl <- mutate(d_trawl,
  DOY = lubridate::yday(date),
  DOY_scaled = arm::rescale(lubridate::yday(date)),
  DOY_scaled2 = arm::rescale(lubridate::yday(date))^2)
```

EXLORE TEMPERATURE at DEPTH
```{r}
ggplot(d_trawl, aes_string("X", "Y", colour = "temperature_c")) +
    geom_point() +
    facet_wrap(~year) +
    coord_fixed() +
    scale_color_viridis_c()
```

```{r}
ggplot(d_trawl, aes(DOY, temperature_c, colour = -depth, alpha=0.5)) + geom_point() + facet_wrap(~year) 
```

Current temperature model
```{r}
spde <- sdmTMB::make_mesh(d_trawl, c("X", "Y"), n_knots = 800, type = "kmeans")
plot(spde)
```

```{r eval = F}
# spde <- make_spde(d_trawl$X, d_trawl$Y, n_knots = 800)
# m_temp_rw <- sdmTMB(
#   temperature_c ~ 0 + as.factor(year),
#   time_varying = ~ 0 + depth_scaled + depth_scaled2,
#   data = d_trawl,
#   ar1_fields = TRUE, # changed AR1 to true
#   include_spatial = TRUE, 
#   time = "year", spde = spde, 
#   family = gaussian(link = "identity"),
#   nlminb_loops = 2,
#   newton_steps = 1,
#   silent = FALSE
# )
# saveRDS(m_temp_rw, file = (here::here("analysis/tmb-sensor-explore/models/model-temp-all-years-800kn.rds")))
```

New CV model code
```{r eval = F}
# m_temp_cv <- sdmTMB_cv(
#   temperature_c ~ 0 + as.factor(year), 
#   time_varying = ~ 0 + depth_scaled + depth_scaled2,
#   data = d_trawl,
#   ar1_fields = TRUE, # changed AR1 to true
#   include_spatial = TRUE, 
#   time = "year", spde = spde, 
#   family = gaussian(link = "identity"),
#   k_folds = 5,
#   # nlminb_loops = 2,
#   # newton_steps = 1,
#   silent = FALSE
# )
# saveRDS(m_temp_cv, file = (here::here("analysis/tmb-sensor-explore/models/model-temp-all-years-800kn-cv.rds")))

m_temp_cv <- readRDS((here::here("analysis/tmb-sensor-explore/models/model-temp-all-years-800kn-cv.rds")))
m_temp_cv$fold_loglik
m_temp_cv$sum_loglik
m_temp_cv$max_gradients
```

Check predictions against raw data
```{r}
m_temp_rw <- readRDS(here::here("analysis/tmb-sensor-explore/models/model-temp-all-years-800kn.rds"))

# m_temp_rw <- sdmTMB:::update_model(m_temp_rw)

predictions <- predict(m_temp_rw)
predictions$residuals <- residuals(m_temp_rw)
cor(predictions$est, predictions$temperature_c)^2 
sum(abs(predictions$residuals))

# 2908.879-2789.322
# 119.557/2908.879 # 4% reduction in abs errors
```

```{r eval=F}
# test against ROMS
events_roms <- readRDS("data/roms_temp_by_events2.rds") %>% select(fishing_event_id, roms, year)
 
predictions <- left_join(predictions, events_roms)

cor(predictions$roms, predictions$est, use = "pairwise.complete.obs")
cor(predictions$roms, predictions$temperature_c, use = "pairwise.complete.obs")

ggplot(predictions, aes(roms, est, colour = -depth)) + geom_point(alpha=0.3) + 
  facet_wrap(~year) + coord_cartesian(xlim = c(2,13), ylim = c(2,13)) +
  geom_abline(intercept = 0, slope = 1) +
  gfplot::theme_pbs()

ggplot(predictions, aes(roms, temperature_c, colour = DOY)) + geom_point(alpha=0.3) +
  facet_wrap(~year) + coord_cartesian(xlim = c(2,13), ylim = c(2,13)) +
  geom_abline(intercept = 0, slope = 1) +
  scale_colour_viridis_c() +
  gfplot::theme_pbs()

ggplot(predictions, aes(DOY, (roms-temperature_c), colour = -depth)) + geom_point(alpha=0.3) +
  facet_wrap(~year) + #coord_cartesian(xlim = c(2,13), ylim = c(2,13)) +
  geom_abline(intercept = 0, slope = 0) +
  scale_colour_viridis_c() +
  gfplot::theme_pbs()

ggplot(predictions, aes(DOY, (est-roms), colour = -depth)) + geom_point(alpha=0.3) +
  facet_wrap(~year) + #coord_cartesian(xlim = c(2,13), ylim = c(2,13)) +
  geom_abline(intercept = 0, slope = 0) +
  scale_colour_viridis_c() +
  gfplot::theme_pbs()

p_nd <- readRDS((here::here("analysis/VOCC/data/predicted-DO-2020-06-20-more2016-roms.rds")))

cor(p_nd$roms_temp, p_nd$temp, use = "pairwise.complete.obs")

ggplot(p_nd, aes(roms_temp, temp, colour = -depth)) + geom_point(alpha=0.04) + 
  facet_wrap(~year) + coord_cartesian(xlim = c(2,13), ylim = c(2,13)) +
  geom_abline(intercept = 0, slope = 1) +
  gfplot::theme_pbs()

```

```{r eval=FALSE}
get_diag(m_temp_rw, response = "temperature_c", variable = "depth_scaled")
```

WOULD SST HELP?

Load and prep SST data
```{r eval=FALSE}
all_sensor <- readRDS(here::here("analysis/tmb-sensor-explore/data/dat-sensor-trawl-meanSST-all.rds"))
d_trawl2 <-all_sensor
# all_sensor <- readRDS(here::here("analysis/tmb-sensor-explore/data/dat-sensor-trawl-processed.rds")) # no SST
# glimpse(all_sensor)
# 
# all_depth <- all_sensor %>%
#   # filter(depth_max>10) %>% # maybe we should filter incase missing depth values also indicate a sensor fail?
#   # filter missing location data and trial year
#   dplyr::filter(!is.na(latitude), !is.na(longitude)) %>%
# 
#   # convert lat and lon to UTMs
#   dplyr::mutate(X = longitude, Y = latitude) %>%
#   gfplot:::ll2utm(., utm_zone = 9) %>% 
# 
#   # interpolate missing depth values
#   dplyr::rename(depth = depth_m) %>%
#   gfplot:::interp_survey_bathymetry()

# d_trawl <- all_depth$data %>% 
#   # remove obvious sensor fails, d_trawl %>% filter(depth_max<10), fishing event ids = 481861, 2179089
#   filter(depth_max>10) %>% 
#   gfplot:::scale_survey_predictors()

d_trawl2 <- d_trawl2[!is.na(d_trawl2$SST), ]
d_trawl2 <- d_trawl2[!is.na(d_trawl2$meanSST), ]

d_trawl2 <- mutate(d_trawl2,
  depth = depth_m,
  DOY = lubridate::yday(date),
  DOY_scaled = arm::rescale(DOY),
  DOY_scaled2 = DOY_scaled^2,
  depth_scaled = arm::rescale(log(depth)),
  SST_scaled = arm::rescale(meanSST),
  depth_scaled2 = depth_scaled^2,
  shallow = ifelse(depth>35,0,1),
  deep = ifelse(depth<35,0,1)
)

d_trawl2 <- d_trawl2[!is.na(d_trawl2$depth_scaled), ]

# d_trawl2[is.na(d_trawl2$shallow), ]
# d_trawl2[is.na(d_trawl2$SST_scaled), ]
```

Explore SST on survey day
```{r eval=FALSE}
ggplot(d_trawl2, aes_string("X", "Y", colour = "SST")) +
    geom_point() +
    facet_wrap(~year) +
    coord_fixed() +
    scale_color_viridis_c()
```

Is bottom temp related to SST in shallower samples?
```{r eval=FALSE}
ggplot(dplyr::filter(d_trawl2, depth <35), aes(SST,temperature_c, colour = -depth)) + geom_point()
ggplot(dplyr::filter(d_trawl2, depth <35), aes(SST,temperature_c, colour = DOY)) + geom_point()
```

Explore mean SST 
```{r eval=FALSE}
ggplot(d_trawl2, aes_string("X", "Y", colour = "meanSST")) +
    geom_point() +
    facet_wrap(~year) +
    coord_fixed() +
    scale_color_viridis_c()
```

```{r eval=FALSE}
ggplot(d_trawl2, aes_string("depth_m", "meanSST", colour = "meanSST")) +
    geom_point() +
    facet_wrap(~ssid, scales = "free") +
    # coord_fixed() +
    scale_color_viridis_c()
```


```{r eval=FALSE}
ggplot(dplyr::filter(d_trawl2, shallow==1), aes(SST_scaled,temperature_c, colour = -depth)) + geom_point()
```


### Try BOOSTED REGRESSION MODEL to check for non-linearity
```{r, eval = FALSE}
library(gbm)
d_trawl2$log_depth <- log(d_trawl2$depth_m)
m <- gbm( temperature_c ~ log_depth + DOY + X + Y, data = d_trawl2, n.trees = 2000, interaction.depth = 3, shrinkage = 0.02)
m2 <- gbm( temperature_c ~ SST_scaled + log_depth + DOY + X + Y, data = d_trawl2, n.trees = 2000, interaction.depth = 3, shrinkage = 0.02)
m3 <- gbm( temperature_c ~ SST_scaled + depth_m + DOY + X + Y, data = d_trawl2, n.trees = 2000, interaction.depth = 3, shrinkage = 0.02)

plot(m,i.var=1) # exp(3.4)= ~30 m is when depth effect begins
plot(m,i.var=2) # strange pattern
plot(m,i.var=3)

plot(m,i.var=1:2) # 50 m depth is when effect of DOY disappears entirely

plot(m2,i.var=1)
plot(m2,i.var=2)
plot(m2,i.var=3)
plot(m2,i.var=4)

plot(m2,i.var=c(2,1))
plot(m2,i.var=c(2,3)) # only < 160 DOY show cooler temps at <30m depths
plot(m2,i.var=c(1,3))

plot(m3,i.var=1:2)

d_trawl2$r <- predict(m, n.trees = 2000) - d_trawl2$temperature_c

ggplot(d_trawl2, aes(depth_scaled, r)) +
  geom_point(alpha=0.4) +
  ylim(-8,8) +
  geom_smooth()

# complex interaction with depth could prove useful at depths shallower than 35m, but for vast majority of depths sampled, DOY and SST should have little effect so test simplier linear models below
```

complex interaction with depth could prove useful at depths shallower than 35m, but for vast majority of depths sampled, DOY and SST should have little effect so test simplier linear models below

### Rerun main model with SST dataset for comparisons
```{r}
spde <- make_mesh(d_trawl2, c("X", "Y"), n_knots = 800)

m_temp_new <- sdmTMB(
  temperature_c ~ 0 + as.factor(year),
  time_varying = ~ 0 + depth_scaled + depth_scaled2,
  data = d_trawl2, spde = spde,
  ar1_fields = TRUE,
  include_spatial = TRUE,
  time = "year",
  family = gaussian(link = "identity"),
  nlminb_loops = 2,
  newton_steps = 1,
  silent = FALSE
)
saveRDS(m_temp_new, file = (here::here("analysis/tmb-sensor-explore/models/model-temp-all-years-800kn-sstdata.rds")))
m_temp_new
AIC(m_temp_new)
```

### try just DOY 
```{r}
spde <- make_mesh(d_trawl2, c("X", "Y"), n_knots = 800)

m_temp_doy_only <- sdmTMB(
  temperature_c ~ 0 + as.factor(year) + DOY_scaled, 
  data = d_trawl2, spde = spde,
  time_varying = ~ 0 + depth_scaled + depth_scaled2,
  ar1_fields = TRUE, 
  include_spatial = TRUE,
  time = "year", 
  family = gaussian(link = "identity"),
  nlminb_loops = 2,
  newton_steps = 1,
  silent = TRUE
)

saveRDS(m_temp_doy_only, file = (here::here("analysis/tmb-sensor-explore/models/model-temp-all-years-800kn-DOY-only.rds")))
tidy(m_temp_doy_only, conf.int = T)
```


### try DOY and SST 
```{r}
spde <- make_mesh(d_trawl2, c("X", "Y"), n_knots = 800)

m_temp_sst <- sdmTMB(
  temperature_c ~ 0 + as.factor(year) + DOY_scaled + SST_scaled, 
  data = d_trawl2, spde = spde,
  time_varying = ~ 0 + depth_scaled + depth_scaled2,
  ar1_fields = TRUE, 
  include_spatial = TRUE,
  time = "year", 
  family = gaussian(link = "identity"),
  nlminb_loops = 2,
  newton_steps = 1,
  silent = TRUE
)

saveRDS(m_temp_sst, file = (here::here("analysis/tmb-sensor-explore/models/model-temp-all-years-800kn-DOY-only.rds")))
tidy(m_temp_sst, conf.int = T)
```

### compare models
```{r}
m_temp_new <- readRDS((here::here("analysis/tmb-sensor-explore/models/model-temp-all-years-800kn-sstdata.rds")))
m_temp_doy_only <- readRDS((here::here("analysis/tmb-sensor-explore/models/model-temp-all-years-800kn-DOY-only.rds")))
m_temp_sst <- readRDS((here::here("analysis/tmb-sensor-explore/models/model-temp-all-years-800kn-SST.rds")))

AIC(m_temp_new, m_temp_doy_only, m_temp_sst)
```


## Plotting predictions from depth only temperature model

```{r }
nd_all <- readRDS(here::here("analysis/VOCC/data/nd_all_synoptic.rds")) %>% filter(year<2019)

unique(nd_all$year)
glimpse(nd_all)
p_nd <- predict(m_temp_rw, newdata = nd_all)

# saveRDS(p_nd, file = "../VOCC/data/predicted_temp_allyears_800kn.rds")
```

```{r}
p_nd <- readRDS("../VOCC/data/predicted_temp_allyears_800kn.rds")

plot_map_raster(p_nd, "est") +
  scale_fill_viridis_c(trans = sqrt) +
  facet_wrap(~year) +
  ggtitle("Prediction (fixed effects + all random effects)")
```

```{r}
plot_facet_map(p_nd, "est", viridis_option = "D",
    raster_limits = c(min(p_nd$est), quantile(p_nd$est, 0.99)),
    transform_col = sqrt
  )
```


```{r}
p_nd1 <- p_nd %>% filter(ssid!=16) %>% filter(ssid!=4)

breaks <- scales::trans_breaks(no_trans[["transform"]], no_trans[["inverse"]],n = 6)
labels <- function(x) format(x, digits = 2, scientific = FALSE)
 
pred_1 <- plot_map_raster(p_nd1, "est") +
  scale_fill_viridis_c(labels = labels, 
    option = "C",
    limits = c(4, 11),
    na.value = "red") +
  facet_wrap(~year) +
  labs(fill = "°C") + 
  ggtitle("Prediction (fixed effects + all random effects)") 
pred_1
```


Time-varying depth 
```{r eval}
# pd <- expand.grid(
#   depth_scaled = seq(min(m_temp_rw$data$depth_scaled),
#     max(m_temp_rw$data$depth_scaled), length.out = 50),
#   year = unique(m_temp_rw$data$year)
# )
# pd$depth_scaled2 <- pd$depth_scaled^2
# 
# # p <- predict(m_temp_rw, newdata = pd, se_fit = TRUE, re_form = NA, xy_cols = c("X", "Y"))
# p <- predict(m_temp_new, newdata = pd, se_fit = TRUE, re_form = NA)
# 
# p$Depth <- exp(p$depth_scaled*0.661 + 5.07)
# p$Temperature <- p$est
# # 
# p$lowCI <- (p$est - 1.96 * p$est_se)
# p$highCI <- (p$est + 1.96 * p$est_se)
# # 
# saveRDS(p, here::here("analysis/tmb-sensor-explore/data/depth-tv-m-temp-rw-800-kn.rds"))
p <- readRDS(here::here("analysis/tmb-sensor-explore/data/depth-tv-m-temp-rw-800-kn.rds"))

ggplot(filter(p, Depth >15 & year >2007), aes(Depth, Temperature,
  ymin = lowCI, 
  ymax = highCI, 
  group = as.factor(year), fill=year, colour = year)) +
  geom_line(size = 0.5, alpha =0.85) +
  # geom_smooth(method= "loess", size = 0.4, alpha =0.85, se =F ) +
  # geom_smooth(span = 0.5, size = 0.4, alpha =0.85, se =F ) +
  scale_fill_viridis_c(option = "C") +
  scale_colour_viridis_c(option = "C") +
  # ylab("DO") +
  geom_ribbon(alpha = 0.2, colour = NA) +
  # scale_y_continuous(limits = c(0,4.5)) +
  scale_x_reverse(limits = c(600,20)) +
  ylim( 2, 15) +
  coord_flip() +
  # scale_x_continuous(limits = c(18,210)) +
  gfplot::theme_pbs() +
  theme(legend.position = c(.8,.4))
ggsave(filename = here::here("analysis/tmb-sensor-explore/figs/depth-tv-m-temp-rw-800-kn.png"), width = 3, height = 2.5)

# ggplot(filter(p, Depth >15 & year == 2018), aes(Depth, Temperature,
#   ymin = (Temperature - 1.96 * est_se), 
#   ymax = (Temperature + 1.96 * est_se))) +
#   geom_line(size = 1.5, alpha =0.85) + 
#   # scale_color_viridis_c(option = "C") +
#   geom_ribbon(alpha=0.2) +
#   scale_x_reverse(limits = c(210,20)) +
#   ylim(5, 15) +
#   coord_flip() +
#   gfplot::theme_pbs() + 
#   theme(legend.position = c(.8,.4))

```


```{r}
p_nd4 <- p_nd %>% filter(ssid==4)
pred_4 <- plot_map_raster(p_nd4, "est") +
  scale_fill_viridis_c(labels = labels, 
    option = "C",
    limits = c(5, 11), 
    na.value = "black")+
  facet_wrap(~year) + 
  theme(legend.position = c(.85,.12)) +
  labs(fill = "°C")
pred_4
```

```{r}
plot_map_raster(p_nd, "est_non_rf") +
  ggtitle("Prediction (fixed effects only)") +
  facet_wrap(~year) +
  scale_fill_viridis_c()
```

```{r}
plot_map_raster(p_nd, "est_rf") +
  ggtitle("Prediction (all random effects only)") +
  facet_wrap(~year) +
  scale_fill_viridis_c()
```

```{r}
(omega_s_all <- plot_map_raster(p_nd, "omega_s") +
  ggtitle("Spatial random effects only") +
    scale_fill_gradient2( low = "Steel Blue 4",
 high = "Red 3", limits = c(-1.5,1.5),
    na.value = "red") +  labs(fill = "") + theme(legend.position = c(0.2, 0.3))
  )

ggsave(filename = here::here("analysis/tmb-sensor-explore/figs/omegas-temp-rw-800-kn.png"), width = 3, height = 3)

omega_s_all

```

```{r}
 plot_map_raster(p_nd, "epsilon_st") +
  ggtitle("Spatiotemporal random effects only") +
  facet_wrap(~year) +   scale_fill_gradient2( low = "Steel Blue 4",
 high = "Red 3", limits = c(-1.5,1.5),
    na.value = "red")
```

```{r}
p_nd <- readRDS("../VOCC/data/predicted_temp_allyears_800kn.rds")

p_nd1 <- p_nd %>% filter(ssid!=16) %>% filter(ssid!=4) %>% filter(year>2007)

(st_1n3 <- plot_map_raster(p_nd1, "epsilon_st") +
  ggtitle("Spatiotemporal random effects") +
  facet_grid(~year) +
   scale_fill_gradient2( low = "Steel Blue 4",
 high = "Red 3", limits = c(-1.5,1.5), #trans = sqrt,
    na.value = "red") +
  labs(fill = "epsilon") + 
  theme(
  legend.position = "none"))

ggsave(filename = here::here("analysis/tmb-sensor-explore/figs/temp-epsilon-1n3.png"), width =6, height = 2)

# png(
#   file = "figs/temp-predictions-1n3.png", 
#   res = 400,
#   units = "in",
#   width = 8, 
#   height = 8
# ) 
# st_1n3
# dev.off()

```

```{r}
p_nd <- readRDS("../VOCC/data/predicted_temp_allyears_800kn.rds")

p_nd4 <- p_nd %>% filter(ssid==4) %>% filter(year>2007)#%>% filter(ssid!=4)
(st_4 <- plot_map_raster(p_nd4, "epsilon_st") +
  #ggtitle(" ") +
  facet_grid(~year) +
     scale_fill_gradient2( low = "Steel Blue 4",
 high = "Red 3", limits = c(-1.5,1.5), #trans = sqrt,
    na.value = "red") +
          labs(fill = " ") + theme( legend.position = "none") )
ggsave(filename = here::here("analysis/tmb-sensor-explore/figs/temp-epsilon-4.png"), width = 6, height = 2)

st_4
```

```{r}
p_nd <- readRDS("../VOCC/data/predicted_temp_allyears_800kn.rds")

p_nd16 <- p_nd %>% filter(ssid==16) %>% filter(year>2007)#%>% filter(ssid!=4)
(st_16 <- plot_map_raster(p_nd16, "epsilon_st") +
  #ggtitle(" ") +
  facet_grid(~year) +
   scale_fill_gradient2( low = "Steel Blue 4",
 high = "Red 3", limits = c(-1.5,1.5),
    na.value = "red") +
  xlim(20,360) + ylim(5850,6050)+ 
  # xlim(65,345) + ylim(5800,6100)+ 
    theme(panel.border = element_blank(), legend.position = "none") )

ggsave(filename = here::here("analysis/tmb-sensor-explore/figs/temp-epsilon-16.png"), width = 6, height = 1)
st_16
```


```{r, eval= F}
png(
  file = "figs/temp-predictions.png", 
  res = 600,
  units = "in",
  width = 11, 
  height = 10
) 

gridExtra::grid.arrange(
  grobs = list(pred_1, st_1n3, omega_s_all, pred_4, st_4, st_16 ),
  widths = c(2, 2, 1.75),
  heights = c(2, 1.35),
  layout_matrix = rbind(c(1, 2, 3),
                        c(4, 5, 6)),
  top = grid::textGrob("Bottom temperature estimates from sdmTMB model")
)

# gridExtra::grid.arrange( nrow = 2, heights = c(2,1.5), 
#   top = grid::textGrob("Dissolved oxygen estimates from sdmTMB model")) 
dev.off()
```

