---
title: "Spatiotemporal models of DO"
author: "Philina English"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: inline
---
# Fit spatial temporal models of bottom DO

```{r setup}
library(tidyverse)
library(gfplot)
library(sdmTMB)
library(gfranges)

plot_map_raster <- function(dat, column = "est") {
    ggplot(dat, aes_string("X", "Y", fill = column)) +
    geom_raster() +
    coord_fixed()+
gfplot::theme_pbs() + theme(
  axis.title = element_blank(), 
  axis.ticks = element_blank(),
  axis.text = element_blank()
  )
}
```

Model diagnostics function
```{r}
get_diag <- function(m, response = "log_do", variable = "depth_scaled", colour_var =  "raw_depth") {
  predictions <- predict(m)
  predictions$residuals <- residuals(m)

  plot_map <- function(dat, column = "est") {
    ggplot(dat, aes_string("X", "Y", colour = column)) +
      geom_point() +
      coord_fixed()+
      gfplot::theme_pbs() 
  }

  g <- plot_map(predictions, "est") +
    scale_colour_viridis_c() +
    ggtitle("Prediction (fixed effects + all random effects)")
  print(g)

  g <- plot_map(predictions, "est_non_rf") +
    ggtitle("Prediction (fixed effects only)") +
    scale_colour_viridis_c()
  print(g)

  g <- plot_map(predictions, "est_rf") +
    ggtitle("All random effects only") +
    scale_colour_gradient2()
  print(g)

  g <- plot_map(predictions, "omega_s") +
    ggtitle("Spatial random effects only") +
    scale_colour_gradient2()
  print(g)

  g <- plot_map(predictions, "epsilon_st") +
    ggtitle("Spatiotemporal random effects only") +
    facet_wrap(~year) +
    scale_colour_gradient2()
  print(g)

  g <- ggplot(predictions, aes_string("est", response)) +
    geom_point(alpha = 0.2) +
    facet_wrap(~year) +
    coord_fixed() +
    geom_abline()+
    gfplot::theme_pbs() 
  print(g)

  g <- ggplot(predictions, aes(est, residuals)) +
    geom_point(alpha = 0.2) +
    geom_smooth()+
    gfplot::theme_pbs() 
  print(g)

g <- ggplot(predictions, aes_string(variable, "residuals", colour = colour_var)) +
    # geom_point(alpha = 0.2) +
    geom_point(alpha = 0.4, size = 0.7) +    
    geom_smooth(colour="grey", size = 0.7) +
    scale_colour_viridis_c(option = "B", direction = -1, begin = 0, end = 0.7, trans= sqrt) +
    facet_wrap(~year, scales = "free_x")+
    gfplot::theme_pbs() + theme(axis.text.x = element_blank(), axis.ticks.x = element_blank())
  # g <- ggplot(predictions, aes_string(variable, "residuals")) +
  #   geom_point(alpha = 0.2) +
  #   geom_smooth() +
  #   facet_wrap(~year)+
  #   gfplot::theme_pbs() 
  print(g)

  g <- ggplot(predictions, aes(X, Y, colour = residuals)) +
    geom_point(alpha = 0.2) +
    coord_fixed() +
    scale_color_gradient2() +
    facet_wrap(~year)+
    gfplot::theme_pbs() 
  print(g)

  aic <- function(m) {
    k <- length(m$model$par)
    nll <- m$model$objective
    2 * k - 2 * (-nll)
  }

  print("R^2:")
  r2 <- cor(predictions$est, predictions[[response]])^2
  print(r2)

  print("")
  print("AIC:")
  print(aic(m))
}
```

Load data
```{r}
all_sensor <- readRDS(here::here("analysis/tmb-sensor-explore/data/all-sensor-data-processed.rds"))
# glimpse(all_sensor)
# 
# all_sensor <- all_sensor %>%
#   mutate(do_mlpl = if_else(year == 2007, NA_real_, do_mlpl),
#     do_mlpl_max = if_else(year == 2007, NA_real_, do_mlpl_max),
#     do_mlpl_min = if_else(year == 2007, NA_real_, do_mlpl_min),
#     do_mlpl_N = if_else(year == 2007, NA_integer_, do_mlpl_N),
#     do_range = if_else(year == 2007, NA_real_, do_range),
#     do_change = if_else(year == 2007, NA_real_, do_change)) %>% select(-akima_depth, -exclude)
# 
# write_csv(all_sensor, here::here("analysis/tmb-sensor-explore/data/all-sensor-data-processed.csv"))


d_trawl <- all_sensor %>%
  # filter missing do data
  dplyr::filter(!is.na(do_mlpl)) %>%
  # remove 2007 data because clearly faulty or scaled differently
  dplyr::filter(year > 2007) %>%
  # add day of year variable
  mutate(
    DOY = lubridate::yday(fe_event_start), temp = temperature_c,
    raw_depth = depth, depth = log(depth), log_do = log(do_mlpl)
  ) %>%
  # scale potential covariates across all surveys
  scale_predictors(predictors = c(quo(depth), quo(DOY), quo(temp)))

d_trawl <- d_trawl[!is.na(d_trawl$depth), ]
d_trawl <- d_trawl[!is.na(d_trawl$temperature_c), ]

d_trawl <- d_trawl %>%
  mutate(exclude = if_else(do_mlpl > 8, 1, 0)) %>%
  filter(exclude != 1)

# glimpse(d_trawl)
```

# Data exploration
Check range of depths and DO sampled
```{r}
paste("depth")
range(d_trawl$raw_depth)
paste("DO")
range(d_trawl$do_mlpl)
```


```{r}
ggplot(d_trawl, aes(X, Y, colour = do_mlpl)) +
  geom_point() +
  facet_wrap(~year) +
  scale_color_viridis_c()
```

```{r}
ggplot(d_trawl, aes(X, Y, colour = temp)) +
  geom_point() +
  facet_wrap(~year) +
  scale_color_viridis_c()
```

```{r}
ggplot(filter(d_trawl, depth_m_max < 80), aes(DOY, log_do, colour = depth)) +
  geom_point() +
  facet_wrap(~year) +
  scale_color_viridis_c()
ggplot(filter(d_trawl, depth_m_max > 80 & depth_m_max < 120), aes(DOY, log_do, colour = depth)) +
  geom_point() +
  facet_wrap(~year) +
  scale_color_viridis_c()
```

```{r}
ggplot(d_trawl, aes(depth, do_mlpl, colour = DOY, size = sqrt(do_change))) +
  geom_point() +
  facet_wrap(~year) +
  scale_color_viridis_c()
```

```{r}
ggplot(d_trawl, aes(raw_depth, temp, colour = DOY, size = sqrt(temp_range))) +
  geom_point() +
  facet_wrap(~year) +
  scale_color_viridis_c()
```

```{r}
ggplot(d_trawl, aes(temp, log_do, colour = DOY, size = sqrt(temp_range))) +
  geom_point() +
  facet_wrap(~year) +
  scale_color_viridis_c()
```

```{r}
ggplot(filter(d_trawl, ssid == 4), aes(DOY, log_do, colour = temp)) +
  geom_point() +
  facet_grid(ssid ~ year, scales = "free") +
  scale_color_viridis_c()
```

```{r}
ggplot(filter(d_trawl, ssid == 4), aes(DOY, temp, colour = temp)) +
  geom_point() +
  facet_grid(ssid ~ year, scales = "free") +
  scale_color_viridis_c()
```

```{r}
ggplot(filter(d_trawl, ssid == 4 & !(year == 2016 & DOY > 149)), aes(X, Y, colour = log_do)) +
  geom_point() +
  facet_grid(ssid ~ year, scales = "free") +
  scale_color_viridis_c()
```

```{r}
ggplot(filter(d_trawl, year == 2016), aes((temp), log(do_mlpl), colour = as.factor(ssid))) +
  geom_point() +
  # facet_wrap(~year) +
  scale_color_viridis_d(begin = 0.65)
```

```{r}
ggplot(filter(d_trawl, year == 2017), aes(x = (temp), log(do_mlpl), colour = as.factor(ssid))) +
  geom_point() +
  # facet_wrap(~year) +
  scale_color_viridis_d(end = 0.35)
```

```{r}
ggplot(d_trawl, aes(DOY, -depth, colour = do_mlpl)) + geom_point() + facet_wrap(~year) +
  scale_color_viridis_c() + ylab("-log(depth)")
```

```{r}
hist(d_trawl$do_mlpl)
# log do_mlpl to allow gaussian
hist(d_trawl$log_do)
```

# Define spatial and temporal components to include in model
Remove most samples from WCVI in 2016 due to extreme values and make mesh
```{r}
d_trawl1 <- d_trawl %>% filter(!(year == 2016 & ssid == 4 & DOY > 149))

spde <- make_spde(d_trawl1$X, d_trawl1$Y, n_knots = 800)
plot_spde(spde)
```

# Define and run model
Current best model of DO
```{r eval=FALSE}

# do_model_all_DOY <- readRDS((here::here("analysis/tmb-sensor-explore/models/model-do-without-wcvi2016b-800kn.rds")))
d_trawl1 <- do_model_all_DOY$data
spde <- make_mesh(d_trawl1, xy_cols=c("X", "Y"), n_knots = 800, type = "kmeans")
plot(spde)
do_model_all_DOY <- sdmTMB::sdmTMB(
  log_do ~ 0 + as.factor(year) + temp_scaled + temp_scaled2 + DOY_scaled,
  data = d_trawl1,
  time_varying = ~ 0 + depth_scaled + depth_scaled2,
  time = "year",
  spde = spde,
  family = gaussian(link = "identity"),
  ar1_fields = TRUE,
  include_spatial = TRUE,
  nlminb_loops = 2,
  newton_steps = 1,
  silent = FALSE
)

saveRDS(do_model_all_DOY, file = (here::here(
  paste0(
    "analysis/tmb-sensor-explore/models/model-do-without-wcvi2016b-",
    "800kn", # Sys.Date(),
    "-update.rds"
  )
)))
```

# Check diagnostics
```{r eval=T}
# do_model_all_DOY <- readRDS((here::here("analysis/tmb-sensor-explore/models/model-do-without-wcvi2016-depth3.rds"))) # 500 knots, poly-3 of depth
# do_model_all_DOY <- readRDS((here::here("analysis/tmb-sensor-explore/models/model-do-without-wcvi2016-depth2.rds"))) # 500 knots, poly-2 of depth
# do_model_all_DOY <- readRDS((here::here("analysis/tmb-sensor-explore/models/model-do-without-wcvi2016-800kn.rds"))) # 800 knots
do_model_all_DOY_old <- readRDS((here::here("analysis/tmb-sensor-explore/models/model-do-without-wcvi2016b-800kn.rds"))) # add in some WCVI 2016 data
do_model_all_DOY <- readRDS((here::here("analysis/tmb-sensor-explore/models/model-do-without-wcvi2016b-800kn-update.rds"))) # rerun in new format. No other changes
# do_model_all_DOY <- sdmTMB:::update_model(do_model_all_DOY)
get_diag(do_model_all_DOY, response = "log_do", variable = "depth_scaled", colour_var =  "raw_depth")

get_diag(do_model_all_DOY, response = "log_do", variable = "DOY_scaled", colour_var =  "raw_depth")
get_diag(do_model_all_DOY, response = "log_do", variable = "temp_scaled", colour_var =  "raw_depth")
```

```{r eval=FALSE}
predictions <- predict(do_model_all_DOY)
predictions$residuals <- residuals(do_model_all_DOY)

predictions$abs <- exp(abs(predictions$residuals))
pred_rows <- filter (predictions, abs != "Inf")
sum(pred_rows$abs) # sum absolute error, divided by nrow for mean absolute error
# 19719.73-17459.49 # difference in absolute error between 500 and 800 knots
# 2260.24/19719.73  # 11% reduction in abs errors
```

# DO predictions
For whole grid using quadratic of predicted temperature values and mean DOY
```{r eval=FALSE}
model1 <- readRDS(here::here("analysis/tmb-sensor-explore/models/model-temp-all-years-800kn.rds"))
model2 <- readRDS(here::here("analysis/tmb-sensor-explore/models/model-do-without-wcvi2016b-800kn.rds"))

nd_all <- readRDS(here::here("analysis/VOCC/data/nd_all_synoptic.rds")) %>% filter(year < 2019)

pred_temp <- predict(model1, newdata = nd_all)

predtemp <- pred_temp %>%
  mutate(
    temp = est,
    temp_omega = omega_s,
    temp_epsilon = epsilon_st,
    temp_scaled = (est - model2$data$temp_mean[1]) / model2$data$temp_sd[1],
    temp_scaled2 = (temp_scaled)^2
  ) %>%
  select(-est, -est_non_rf, -est_rf, -omega_s, -zeta_s, -epsilon_st)
predtemp <- predtemp %>% filter(year > 2007)
predtemp$DOY_scaled <- 0

# make DO predictions
pred_do <- predict(model2, newdata = predtemp)

# rename and back transform climate variables
pred_do$log_do <- pred_do$est
pred_do$do_est <- exp(pred_do$log_do)

saveRDS(pred_do, file = here::here(paste0("analysis/VOCC/data/predicted-DO-", Sys.Date(), "-more2016.rds")))
```


Time-varying depth 
```{r eval = F}
# pd <- expand.grid(
#   temp_scaled = 0,
#   temp_scaled2 = 0,
#   DOY_scaled = 0, 
#   depth_scaled = seq(min(do_model_all_DOY$data$depth_scaled),
#     max(do_model_all_DOY$data$depth_scaled), length.out = 30),
#   year = unique(do_model_all_DOY$data$year)
# )
# pd$depth_scaled2 <- pd$depth_scaled^2
# 
# p <- predict(do_model_all_DOY, newdata = pd, se_fit = TRUE, re_form = NA)
# 
# p$DO <- exp(p$est)
# p$lowCI <- exp(p$est - 1.96 * p$est_se)
# p$highCI <- exp(p$est + 1.96 * p$est_se)
# 
# p$Depth <- exp(p$depth_scaled*do_model_all_DOY$data$depth_sd[1]+do_model_all_DOY$data$depth_mean[1])
# saveRDS(p, here::here("analysis/tmb-sensor-explore/data/depth-tv-m-do-DOY-800kn.rds"))

p <- readRDS(here::here("analysis/tmb-sensor-explore/data/depth-tv-m-do-DOY-800kn.rds"))

ggplot(filter(p, year != 2007), aes(Depth, exp(est), 
  ymin = lowCI,
  ymax = highCI,
  group = as.factor(year), fill = year, colour = year)) +
  geom_line(size = 0.5, alpha =0.85) +
  # geom_smooth(method= "loess", size = 0.4, alpha =0.85, se =F ) +
  # geom_smooth(span = 0.5, size = 0.4, alpha =0.85, se =F ) +
  scale_fill_viridis_c(option = "C") +
  scale_colour_viridis_c(option = "C") +
  ylab("DO") +
  geom_ribbon(alpha = 0.2, colour = NA) +
  scale_y_continuous(limits = c(0.5,5)) +
  scale_x_reverse(limits = c(650,20)) +
  coord_flip() +
  # scale_x_continuous(limits = c(18,210)) +
  gfplot::theme_pbs() +
  theme(legend.position = c(.8,.4))
ggsave(filename = here::here("analysis/tmb-sensor-explore/figs/depth-tv-m-do-DOY-800-kn.png"), width = 3, height = 2.5)
```

Temperature effect
```{r}
### temp
min(do_model_all_DOY$data$temp_scaled)
# 
# pd <- expand.grid(
#   temp_scaled = seq(min(do_model_all_DOY$data$temp_scaled) + 0.1,
#     max(do_model_all_DOY$data$temp_scaled) - 0.1, length.out = 20),
#   DOY_scaled = 0, 
#   depth_scaled = 0,
#   depth_scaled2 = 0,
#   # year = c(2017L, 2018L)
#   year = unique(do_model_all_DOY$data$year) # seems to need multiple years? why?
# ) %>% filter(year>2016)
# # pd$depth_scaled2 <- pd$depth_scaled^2
# pd$temp_scaled2 <-  pd$temp_scaled^2
# # p <- predict(do_model_all_DOY, newdata = pd, se_fit = TRUE, re_form = NA, xy_cols = c("X", "Y"))
# p <- predict(do_model_all_DOY, newdata = pd, se_fit = TRUE, re_form = NA)
# 
# p$DO <- exp(p$est)
# p$lowCI <- exp(p$est - 1.96 * p$est_se)
# p$highCI <- exp(p$est + 1.96 * p$est_se)
# 
# 
p$Temperature <- do_model_all_DOY$data$temp_sd[1]*p$temp_scaled+do_model_all_DOY$data$temp_mean[1]
saveRDS(p, here::here("analysis/tmb-sensor-explore/data/temp-m-do-DOY-800-kn.rds"))
p <- readRDS(here::here("analysis/tmb-sensor-explore/data/temp-m-do-DOY-800-kn.rds"))

ggplot(filter(p, Temperature < 15 & year <2018), aes(Temperature, DO, 
  ymin = lowCI, 
  ymax = highCI)) +
  geom_line(size = 1.5, alpha =0.85) + 
  # scale_color_viridis_c(option = "C") +
  geom_ribbon(alpha=0.2) +
  # ylim(20, 210) +
  gfplot::theme_pbs() + 
  theme(legend.position = c(.8,.4))

ggsave(filename = here::here("analysis/tmb-sensor-explore/figs/temp-m-do-DOY-800-kn.png"), width = 3, height = 2.5)

```


Seasonal effect
```{r}
# pd <- expand.grid(
#   temp_scaled = 0,
#   temp_scaled2 = 0,
#   DOY_scaled = seq(min(do_model_all_DOY$data$DOY_scaled) + 0.1,
#     max(do_model_all_DOY$data$DOY_scaled) - 0.1, length.out = 5),
#   depth_scaled = 0,
#   depth_scaled2 = 0,
#   year = unique(do_model_all_DOY$data$year) # seems to need multiple years? why?
# ) 
# 
# p <- predict(do_model_all_DOY, newdata = pd, se_fit = TRUE, re_form = NA)
# 
# p$DO <- exp(p$est)
# p$lowCI <- exp(p$est - 1.96 * p$est_se)
# p$highCI <- exp(p$est + 1.96 * p$est_se)
# 
# p$DOY <- p$DOY_scaled*do_model_all_DOY$data$DOY_sd[1]+ do_model_all_DOY$data$DOY_mean[1]
# 
# saveRDS(p, here::here("analysis/tmb-sensor-explore/data/DOY-do-800-kn.rds"))
p <- readRDS(here::here("analysis/tmb-sensor-explore/data/DOY-do-800-kn.rds"))

ggplot(filter(p), aes(DOY, DO, 
  ymin = lowCI, 
  ymax = highCI, 
  group= as.factor(year), fill = year, colour = year)) +
  geom_line(size = 1.5, alpha =0.85) + 
  scale_fill_viridis_c(option = "C") +
  scale_color_viridis_c(option = "C") +
  geom_ribbon(alpha = 0.05, colour = NA) +
  # ylim(20, 210) +
  coord_cartesian(ylim = c(1,5)) +
  gfplot::theme_pbs()# + 
  # theme(legend.position = c(.8,.7))

ggsave(filename = here::here("analysis/tmb-sensor-explore/figs/do-DOY-800-kn.png"), width = 3, height = 2.5)
```



Plot predictions from saved DO predictions file
```{r}
p_nd <- readRDS((here::here("analysis/VOCC/data/predicted-DO-2020-06-20-more2016.rds")))
p_nd <- readRDS("~/github/dfo/gfranges/analysis/VOCC/data/predicted-DO-2020-06-20-more2016-roms.rds")
plot_map_raster(p_nd, "do_est") +
  scale_fill_viridis_c(trans = "log") +
  facet_wrap(~year) +
  ggtitle("Prediction (fixed effects + all random effects)")
```

Plot each survey separately
```{r}
p_nd1 <- p_nd %>%
  filter(ssid != 16) %>%
  filter(ssid != 4)

breaks <- scales::trans_breaks(no_trans[["transform"]], no_trans[["inverse"]], n = 6)
labels <- function(x) format(x, digits = 2, scientific = FALSE)

pred_1 <- plot_map_raster(p_nd1, "do_est") +
  scale_fill_viridis_c(
    labels = labels, breaks = c(0, 2, 4, 6, 8),
    limits = c(0, 7),
    na.value = "gold"
  ) +
  facet_wrap(~year) +
  labs(fill = "ml/L DO") +
  ggtitle("Prediction (fixed effects + all random effects)") +
  theme(legend.position = c(.85, .25))
pred_1
```

```{r}
p_nd4 <- p_nd %>% filter(ssid == 4) # %>% filter(year!=2016)
pred_4 <- plot_map_raster(p_nd4, "do_est") +
  scale_fill_viridis_c(
    labels = labels, breaks = c(0, 2, 4, 6, 8), limits = c(0, 7),
    na.value = "red"
  ) +
  facet_wrap(~year) +
  labs(fill = "ml/L DO") +
  # ggtitle(" ")+
  theme(legend.position = "none")
pred_4
```


```{r}
p_nd16 <- p_nd %>% filter(ssid == 16) # %>% filter(year!=2016)
pred_16 <- plot_map_raster(p_nd16, "do_est") +
  scale_fill_viridis_c(
    labels = labels, breaks = c(0, 2, 4, 6, 8), limits = c(0, 7),
    na.value = "red"
  ) +
  facet_wrap(~year) +
  labs(fill = "ml/L DO") +
  # ggtitle(" ")+
  theme(legend.position = "none")
pred_16
```

```{r}
plot_map_raster(p_nd, "est_non_rf") +
  ggtitle("Prediction (fixed effects only)") +
  facet_wrap(~year) +
  scale_fill_viridis_c()
```

```{r}
plot_map_raster(p_nd, "est_rf") +
  ggtitle("Prediction (all random effects only)") +
  facet_wrap(~year) +
  scale_fill_gradient2(
    high = "Steel Blue 4",
    low = "Red 3"
  ) # , limits = c(-0.65,1)
# scale_fill_viridis_c()
```

```{r}
p_nd <- readRDS("~/github/dfo/gfranges/analysis/VOCC/data/predicted-DO-2020-06-20-more2016-roms.rds")

(omega_s_all <- plot_map_raster(p_nd, "omega_s") +
  ggtitle("Spatial random effects only") +
  scale_fill_gradient2(
    # high = "Steel Blue 4", low = "Red 3",
    high = "gold", low = "darkcyan",
    limits = c(-0.65, 1)
  ) +
  labs(fill = " ") +
  theme(legend.position = c(.2, .3)))
ggsave(filename = here::here("analysis/tmb-sensor-explore/figs/omegas-do-rw-800-kn-yg.png"), width = 3, height = 3)
omega_s_all
```

```{r}
plot_map_raster(p_nd, "epsilon_st") +
  ggtitle("Spatiotemporal random effects only") +
  facet_wrap(~year) +
  scale_fill_gradient2(
    high = "Steel Blue 4",
    low = "Red 3"
  )
```

```{r}
p_nd <- readRDS("~/github/dfo/gfranges/analysis/VOCC/data/predicted-DO-2020-06-20-more2016-roms.rds")

p_nd1 <- p_nd %>%
  filter(ssid != 16) %>%
  filter(ssid != 4)

(st_1n3 <- plot_map_raster(p_nd1, "epsilon_st") +
  ggtitle("Spatiotemporal random effects") +
  facet_grid(~year) +
  scale_fill_gradient2(
    # high = "Steel Blue 4", low = "Red 3", 
    high = "gold", low = "darkcyan",
    limits = c(-0.65, 1)
  ) +
  labs(fill = " ") + theme( legend.position = "none") )

ggsave(filename = here::here("analysis/tmb-sensor-explore/figs/do-epsilon-1n3-yg.png"), width = 6, height = 2)
# st_1n3
```

```{r}
p_nd <- readRDS("~/github/dfo/gfranges/analysis/VOCC/data/predicted-DO-2020-06-20-more2016-roms.rds")

p_nd4 <- p_nd %>% filter(ssid == 4) # %>% filter(year!=2016)
(st_4 <- plot_map_raster(p_nd4, "epsilon_st") +
  # ggtitle(" ") +
  facet_grid(~year) +
  scale_fill_gradient2(
    # high = "Steel Blue 4", low = "Red 3", 
    high = "gold", low = "darkcyan",
    limits = c(-0.65, 1)
  ) +
  labs(fill = "epsilon") + theme( legend.position = "none") )

ggsave(filename = here::here("analysis/tmb-sensor-explore/figs/do-epsilon-4-yg.png"), width = 6, height = 2)
# st_4
```

```{r}
p_nd <- readRDS("~/github/dfo/gfranges/analysis/VOCC/data/predicted-DO-2020-06-20-more2016-roms.rds")

p_nd16 <- p_nd %>% filter(ssid == 16) # %>% filter(ssid!=4)
(st_16 <- plot_map_raster(p_nd16, "epsilon_st") +
  # ggtitle(" ") +
  facet_grid(~year) +
  scale_fill_gradient2(
    # high = "Steel Blue 4", low = "Red 3", 
    high = "gold", low = "darkcyan",
    limits = c(-0.65, 1)
  ) +
  xlim(20,360) + ylim(5850,6050)+ 
  # xlim(65,345) + ylim(5800,6100)+ 
    theme(panel.border = element_blank(), legend.position = "none") )

ggsave(filename = here::here("analysis/tmb-sensor-explore/figs/do-epsilon-16-yg.png"), width = 6, height = 1)
# st_16
```

```{r}
p_nd <- readRDS("~/github/dfo/gfranges/analysis/VOCC/data/predicted-DO-2020-06-20-more2016-roms.rds")

ggplot(p_nd, aes(roms_temp, temp, colour = depth)) +
  geom_point(alpha = 0.1, size = 0.5) + 
  scale_color_viridis_c(option = "B", begin = 0, end = 0.7, direction = -1, trans= sqrt) + 
  xlim(2,15) +
  ylim(2,15) +
  geom_abline(intercept = 0, slope = 1, colour="grey") +
  ylab("Mean May-August temperature from CTD only model ") +
  xlab("Mean April-September temperature from ROMS model ") +
  gfplot::theme_pbs() + 
    theme(legend.position = "none") 
ggsave(filename = here::here("analysis/tmb-sensor-explore/figs/roms.png"), width = 4.5, height =4.5)

```



Save selection of prediction plots
```{r, eval= F}
png(
  file = "figs/do-predictions-without-wcvi2016.png",
  res = 600,
  units = "in",
  width = 11,
  height = 6.5
)

gridExtra::grid.arrange(
  grobs = list(pred_1, st_1n3, omega_s_all, pred_4, st_4, st_16),
  widths = c(2, 2, 1.75),
  heights = c(2, 1.5),
  layout_matrix = rbind(
    c(1, 2, 3),
    c(4, 5, 6)
  ),
  top = grid::textGrob("Dissolved oxygen estimates from sdmTMB model")
)
dev.off()
```
